%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{soul}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Vidit Jain} \\ \vspace{1pt}
  \small +1 951-866-3558 $|$ \href{mailto:vjain018@ucr.edu}{\ul{vjain018@ucr.edu}} $|$
  \href{https://linkedin.com/in/viditjain1}{\ul{Linkedin}} $|$
  \href{https://github.com/JainVidit12}{\ul{GitHub}}
\end{center}



%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{State Street Global Advisors}{Oct 2018 -- Sep 2022}
{Quantitative Developer - Senior Associate 2}{Bengaluru, India}
\resumeItemListStart
\resumeItem{Designed the streaming data flow to deliver live performance on trade baskets, enabling portfolio managers to execute bespoke strategies at scale. Used AWS MSK}
\resumeItem{Built batch ELT pipelines to onboard new datasets to OLAP databases, including unit testing and data quality monitoring.}
\resumeItem{Designed, Built and deployed a volume prediction model including continuous monitoring and integration. Reduced trading cost by 30\% during extreme market volatility. Used SparkML.}
\resumeItem{Identified and successfully integrated two new signals into existing strategies after panel regression study, leading to excess return of 10 basis points on cumulative AUM USD 10 Billion.}
\resumeItem{Tools used: Airflow, PySpark, AWS, Postgres, Kafka}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
\resumeSubSubheading
{Quantitative Developer - Senior Associate}{Bengaluru, India}
\resumeItemListStart
\resumeItem{Optimized backtesting data flow using AWS elasticache lazy loading, reducing subsequent reads query time by 70\%}
\resumeItem{Led initiative to leverage intraday data including data cleaning, ETL and subsequent research. Led to 30\% less tracking error breaches in equity portfolios.}
\resumeItemListEnd

% -------------------------------------------
\resumeSubSubheading
{Quantitative Developer - Associate}{Bengaluru, India}
\resumeItemListStart
\resumeItem{Added security features and improved memory safety for the internal equity risk model and order management systems using new C++(14) features.}
\resumeItem{Automated existing processes and tasks using Python(Pandas, Numpy) and FactSet API.}
\resumeItemListEnd



\resumeSubheading
{Zenatix Solutions}{Jul 2018 -- Sep 2018}
{Software Development Engineer}{Gurugram, India}
\resumeItemListStart
\resumeItem{Built an analytics dashboard to monitor power consumption and cold storage temperature metrics using ReactJS, DynamoDB, and NodeJS.}

\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of California Riverside}{Riverside, CA}
{MS in Computer Engineering $|$ GPA 4.0 / 4.0}{Jan. 2023 -- Mar 2024}
\resumeSubheading
{Indian Institute of Technology}{Jodhpur, India}
{Bachelor's in Electrical Engineering $|$ GPA 7.5 / 10.0}{Aug. 2014 -- May 2018}
\resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Online Optimization using LLMs and Reinforcement Learning} $|$ \emph{Master's Project} }
{Sep 2023 -- Present}
\resumeItemListStart
\resumeItem{Built multi-agent LLM framework to adjust optimization parameters using natural languate input.}
\resumeItem{Currently building Reinforcement learning policy to dynamically relax constraints based on changes in the problem}
\resumeItem{Multi-Agent pipeline with Retrieval Augmented Generation (RAG) and safeguard mechanism to ensure reliability}
\resumeItem{Built evaluation dataset also using LLM, used async programming to optimize it.}
\resumeItem{Used OpenAI API and PyAutogen libraries}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Open Source Contributions} }
{}
\resumeItemListStart
\resumeItem{\href{https://github.com/run-llama/llama_index}{\ul{Llama\_index}}: Developed methods to optimize token consumption}
\resumeItem{\href{https://github.com/avhz/RustQuant}{\ul{RustQuant}}: Developed pricing models for fixed income instruments in Rust}
\resumeItemListEnd
\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Languages}{: Python, C++, Java, SQL(Postgres, PL/pgSQL, MySQL)} \\
                \textbf{Database/Frameworks}{: Apache Spark, SparkML, Apache Airflow, Kafka, Git} \\
                \textbf{Cloud}{: AWS} \\
                \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Pytorch}
          }}
\end{itemize}

%
%-----------Awards and Recognitions-----------
\section{Awards and Recognitions }
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
  {Runner up 2015 \& 2016 IIT Jodhpur Microsoft code.fun.do hackathon. Built mobile apps for windows phone using Azure. } \\
  {2016 \& 2017 Merit-Cum-Means scholarship covering 100\% tution fees awarded by Govt. of India}

  }}
\end{itemize}

%-----------Coursework-----------
% \section{Courses}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Graduate}{Machine Learning, Deep Learning, Real Time Systems, High Performance Computing, GPU Architecture and Parallel Programming, Natural Language Processing, Data Mining Techniques, Advanced Operating Systems.} \\
%      {2016 \& 2017 Merit-Cum-Means scholarship covering 100\% tution fees awarded by Govt. of India} \\

%     }}
%  \end{itemize}


%-------------------------------------------
\end{document}
